Dish: Distribution-oblivious Shell Scripting

### 2019-11-23 pldi/draft.tex
Checkpoint to revert

At a high level, we are interested in understanding whether \sys can indeed scale pipelines out automatically and correctly.
To achieve this, we use a combination of micro- and macro-benchmarks, most of which were collected from prior literature and online repositories.
Micro-benchmarks~\sx{micro} are one-off, simple one-line pipelines that take a few seconds to write (usually interactively);
  such pipelines are usually composed interactively to solve a task at hand, test a hypothesis, or ``smoke out bugs''~\cite{bentley1986literate}---but, with \sys, applied to very large data sets.
These pipelines are taken from real, often striking~\cite{}, use cases and have the benefit of highlighting stress on a handful of stages, precisely due to their small size.

@@

@@

\subsection{Macro-benchmark: Weather Analysis}

@@

@@

\subsection{Macro-benchmark: Web Crawling}

\subsection{Macro-benchmark: Bioinformatics Transform}

>>>>

At a high level, we are interested in understanding whether \sys can indeed scale pipelines out automatically and correctly.
To achieve this, we use a combination of micro- and macro-benchmarks, most of which were collected from prior literature and online repositories.
Micro-benchmarks~\sx{micro} are one-off, simple one-line pipelines that take a few seconds to write (usually interactively);
  such pipelines are usually composed interactively to solve a task at hand, test a hypothesis, or ``smoke out bugs''~\cite{bentley1986literate}---but, with \sys, applied to very large data sets.
These pipelines are taken from real use cases (often from the literature~\cite{bentley1985spelling, bentley1985spelling}), and, precisely due to their small size, have the benefit of highlighting stress on a handful of stages.

@@

Spell program~\cite{bentley1985spelling}

\ttt{wf}
Word-count~\cite{bentley1986literate}

\ttt{top-n}

@@

\subsection{Macro-benchmark: Weather Analysis}
\label{macro1}

@@

The pipeline starts with a few stages in \sta  that generate URLs;
  these URLs point to index files, each one of which contains pointers 
The stream of index files is analyzed (4 stages) to extract the URLs of the compressed data files.
It is then passed again through a download command
After downloading and uncompressing these files, the stream is analyzed to extract the maximum temperature.

A less obvious lesson from this case was that  
First, large, complex pipelines enable significant freedom in how to express some stages.
Several stages in the original program are compressed into a single \ttt{awk} script;
  unfortunately, \ttt{awk} is too general to have a helpful distributability signature.
For example, the \ttt{sort} command at the end is an expensive version of extracting the maximum element;
  this could have been expressed with a simple \ttt{awk} script that only keeps track of the max.

The Hadoop program 
Hadoop 3.2.1
openjdk 11.0.5
ruby 2.5.5p157

few different ways to write some phases, 
  for example, 
A large pipeline resulted in a couple of 
An interesting lesson here was that there are multiple
First, longer pipelines can be written in multiple ways
It is worth noting
These are

@@

\subsection{Macro-benchmark: Bioinformatics Transform}
\label{macro3}

\subsection{Macro-benchmark: Web Crawling}
\label{macro2}
